$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2014-03-09 JournalToSubmit2013/modelingFlyingPig.tex
starting to address section FlyingPig .. 10/04/2014

\begin{figure}[t]
\centering
\includegraphics[width=1.0\textwidth]{figs/BPMN_GCP.pdf}

{\color{red} Javier: Please change \underline{Asses} by \underline{Assess}. --M}
\caption{BPMN model for \FlyingPig.\label{fig:BPMNmodel}}
\end{figure}

The BPMN model for \FlyingPig\ is devised to better understand the process in which the value exchanges occur.
Figure~\ref{fig:BPMNmodel} shows the BPMN model\footnote{\color{red} Details on BPMN (Business Process Management Notation) can be found in http://www.bpmn.org/.} for the \FlyingPig\ scenario. 
The model includes two pools representing the \textsl{ORCA} system and the \textsl{Brokers}. 
Brokers have two lanes, the client \textsl{Company} and a \textsl{User}. 
The user is a contact member of the company, who will coordinate the assessment process. 
This process will involve other members of the company as well.

@@

In Section~\ref{sec:modelingWithPISODM} we defined three models at the PIM level.
These models are built next, for the \FlyingPig\ scenario.

@@

{\color{red} Anything else here? --M}

@@

The model presented in Figure~\ref{fig:PiPEWSModel} is the result of translating the previous model into service composition code.
Notice that the workflow for \FlyingPig\ is implemented by using the constructors present in BPEL~\cite{BPEL}, with the addition of the notion of \textit{contract}.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1.0\textwidth]{figs/BPMN_GCP.pdf}
\caption{BPMN model for \FlyingPig.\label{fig:BPMNmodel}}
\end{figure}

The BPMN model for \FlyingPig\ is devised to better understand the process in which the value exchanges occur.
Figure~\ref{fig:BPMNmodel} shows the BPMN model
%\footnote{\color{red} Details on BPMN (Business Process Management Notation) can be found in http://www.bpmn.org/.} 
for the \FlyingPig\ scenario. 
The model includes two pools representing the \textsl{ORCA} system and the \textsl{Brokers}. 
Brokers have two lanes, the client \textsl{Company} and a \textsl{User}. 
The user is a contact member of the company, who will coordinate the assessment process. 
This process will involve other members of the company as well.

@@

%In Section~\ref{sec:modelingWithPISODM} we defined three models at the PIM level.
The $\pi$-SOD-M models of the PIM level  for the \FlyingPig\ scenario are presented next.

@@

%{\color{red} Anything else here? --M}

@@

The  PSM models of our methodology result of translating the previous model into service composition code.
Notice that the workflow for \FlyingPig\ is implemented by using the constructors present in BPEL~\cite{BPEL}, with the addition of the notion of \textit{contract}.
